The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-04-05 manuscript/manuscript.qmd
Add super initial outline

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
bibliography: references.bib
link-citations: true
format: 
  html:
    toc: true
  pdf: default
  docx: default
language: 
  title-block-published: "Latest version"
---

@@

## References

>>>>

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
bibliography: references.bib
link-citations: true
format: 
  html:
    toc: true
    citeproc: false
    filters: 
      - "_extensions/andrewheiss/wordcount/citeproc.lua"
      - "_extensions/andrewheiss/wordcount/wordcount.lua"
  pdf: default
  docx: default
language: 
  title-block-published: "Latest version"
---

@@

# Introduction

ONGO law, what has it meant for ONGOs—how are they responding?

@FaridLi:2021

Charity law + ONGO law happened at the same time - lots of discussion about what it would mean for ONGOs at the time - lots of people looked at the framework of the law, but we don't know what it has actually looked like
Following up with the actual implementation of law

# Context of the ONGO law

How the law works, what it looked like pre-2016/7

# Literature

## Literature on global crackdown on NGOs

Contentiousness, regime stability, other reasons

## Literature on implementation - de jure vs. de facto differences

## Literature on organizational flexibility

# Theory / research questions

- RQ1: Provinces and work field - connects to NGO contentiousness bc everything is noncontentious
- RQ2: Provinces and PSUs - local vs. national - there's variance in local PSUs - flexibility, venue-seeking maybe
- RQ3: Provinces and length of time in country / registration date/year - earlier organizations work in more? - flexibility bc more local knowledge, more interest, more support from government to get registered, etc.

# Data and methods

No control/pre-group - this is all descriptive about the "after" group of ONGOs that all selected themselves into the regulations

multiple_id - either treat it as a random organization effect for the parent org, or weight it, so if there are 8, we weight by 1/8
cn_background = Chinese NGOs

Main assumption: We're interested in the potential to be in other provinces, even if an organization is small now, they want to someday spread out

# Results

TODO: Oxfam and World Vision as short case studies?

# Discussion

# References
